### 2020-01-27 frontmatter.tex
added /safe for recovery.

%-------------------------------------------------------------------------------
% Abstract (English)
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
\begin{abstract}
	Access points  must work. In fact, few cryptographers would disagree with
	the emulation of robots, which embodies the technical principles of
	complexity theory. Hyp, our new application for lossless information, is the
	solution to all of these challenges.
		%
		\keywords{super-lasers, space-stations, The Force, cookies.}
		%
\end{abstract}

%-------------------------------------------------------------------------------
% Abstrakt (Swedish) 
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
\begin{abstrakt}
	\r{A}tkomstpunkter m\r{a}ste arbeta. I sj\"{a}lva verket skulle f\r{a}
	kryptografer h\r{a}ller inte med emulering av robotar, som
	f\"{o}rkroppsligar de tekniska principer av komplexitetsteori. Hyp, v\r{a}r
	nya applikation f\"{o}r f\"{o}rlustfri information är l\"{o}sningen på alla
	dessa utmaningar.
		%
		\nyckelord{super-lasrar, rymdstationer, Kraften, kakor.}
		%
\end{abstrakt}

>>>>

%-------------------------------------------------------------------------------
% Abstract (English)
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
\begin{abstract}
Micron to millimetre sized droplets, precisely generated or sustained in controlled environment, have great potential in myriads of engineering applications
functioning as the basic element to assemble metamaterials, deliver drugs, host surfactant, reduce friction and damp turbulence.
The interaction of droplets from pairwise to collective levels is the most important factor in controlling these processes,
yet little is known about the detailed mechanisms in various nonideal conditions.
The present thesis combines a number of studies aiming to elucidate the physical principles of droplet interactions and suspension flow
using both high- and low-fidelity numerical simulations.

We first study flow-assisted droplet assembly in microfluidic channels, seeking to harness the droplet interactions to produce photonic bandgap materials.
A novel interface-correction level set/ghost fluid method (ICLS/GFM) is developed to directly simulate liquid droplets under depletion forces.
Comparing to previous methods, ICLS/GFM conserves the global mass of each fluid using a simple mass-correction scheme,
accurately computes the surface tension and depletion forces under the same framework,
and has subsequently been applied to investigate the droplet clustering observed in a microfluidic experiment.
Our simulations, supported by theoretical derivations, suggest that the observed fast self-assembly arises from a combination of 
strong depletion forces, confinement-mediated shear alignments of the droplets, and fine-tuned inflow conditions of the microchannel.
However, the interplay of these 3D effects negates a simple droplet interaction model of parametric dependence,
rendering the design of microfluidic chips for photonic crystal fabrications elusive in practice.

The next focus of the thesis is the implementation of a minimal discrete-element lubrication/contact dynamics model for simulation of dense particle suspensions.
Here, the main ingredients include a frame-invariant, short-range lubrication model for spherical particles,
and a soft-core, stick/slide frictional contact model activated when particles overlap.
Furthermore, since contact interactions dominate at high particle concentrations,
we expect the methodology to be applicable for probing the jamming of non-spherical particles and the rheology of foams as well.

Finally, we include two miscellaneous studies concerning
the slippage property of liquid-infused surfaces and droplets statistics in a homogeneous turbulent shear flow.
Overall, results of these simulations provide detailed flow visualisations and qualitative dependence of the target functional on various governing parameters,
facilitating experimental and theoretical investigations to design more robust drag-reducing surfaces and predict droplet distributions in emulsions.

%
\keywords{droplets, suspension, multiphase flow, microfluidics, soft matter, rheology, depletion force, level set, ghost fluid, discrete element.}
%
\end{abstract}

%-------------------------------------------------------------------------------
% Abstrakt (Swedish) 
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
\begin{abstrakt}
Droppar av mikron till millimeter, exakt genererade eller bibehållna i kontrollerad miljö, har stor potential i många olika tekniska applikationer
fungerar som det grundläggande elementet för att montera metamaterial, leverera läkemedel, värda ytaktivt medel, minska friktion och fuktig turbulens.
Interaktion mellan droppar från parvis till kollektivnivå är den viktigaste faktorn för att kontrollera dessa processer,
ändå är lite känt om de detaljerade mekanismerna i olika nonideala förhållanden.
Den här avhandlingen kombinerar ett antal studier som syftar till att belysa de fysiska principerna för droppinteraktioner och suspensionflöde
med både numeriska simuleringar med hög och låg trovärdighet.

Vi studerar först flödesassisterade droppmontering i mikrofluidkanaler och försöker utnyttja droppinteraktioner för att producera fotoniska bandgapmaterial.
En ny gränssnittskorrigeringsnivåuppsättning/spökvätskemetod (ICLS/GFM) är utvecklad för att direkt simulera vätskedroppar under utarmningskrafter.
Jämfört med tidigare metoder sparar ICLS/GFM den globala massan för varje fluid med hjälp av ett enkelt masskorrigeringsschema,
beräknar exakt ytspänningen och utarmningskrafterna under samma ram,
och har sedan applicerats för att undersöka droppklusteringen som observerats i ett mikrofluidiskt experiment.
Våra simuleringar, med stöd av teoretiska härledningar, antyder att den observerade snabba självmonteringen uppstår från en kombination av
starka utarmningskrafter, inneslutningsförmedlade skjuvlinjeringar av dropparna och fininställda inflödesförhållanden för mikrokanalen.
Men samspelet mellan dessa 3D-effekter avskaffar en enkel droppinteraktionsmodell av parametriskt beroende,
vilket gör utformningen av mikrofluidiska chips för fotoniska kristallfabrikationer som är svåra i praktiken.

Nästa fokus för avhandlingen är implementeringen av en minimal diskret-element smörjning/kontaktdynamik-modell för simulering av täta partikelsuspensioner.
Här innehåller huvudingredienserna en ram-invariant smörjningsmodell med kort räckvidd för sfäriska partiklar,
och en friktionskontaktmodell med mjukkärna, stick/slide aktiverad när partiklar överlappar varandra.
Eftersom kontaktinteraktioner dominerar vid höga partikelkoncentrationer,
vi förväntar oss att metodologin också är tillämplig för att undersöka fastklämning av icke-sfäriska partiklar och reologi för skum.

Slutligen inkluderar vi två diverse studier rörande
glidningsegenskapen hos vätska-infunderade ytor och droppstatistik i ett homogent turbulent skjuvflöde.
Sammantaget ger resultaten av dessa simuleringar detaljerade flödesvisualiseringar och kvalitativt beroende av målfunktionen på olika reglerande parametrar,
underlätta experimentella och teoretiska undersökningar för att utforma mer robusta dragreducerande ytor och förutsäga droppfördelningar i emulsioner.
%
\nyckelord{droppar, suspension, flerfasflöde, mikrofluidik, mjukt material, reologi, utarmningskraft, nivåuppsättning, spökvätska, diskret element.}
%
\end{abstrakt}
